The Mass Relations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGN Systems.

### 2020-04-06 manuscript/manuscript.tex
Update manuscript.tex
Update project

Our work, once again, confirmed the fidelity of using strong lensing as a tool to study the scaling relation at high redshift. The lensed AGN host galaxy can be accurately recovered using the state-of-the-art lens modelling technique. Even more, with a higher lens magnification effect, the lensed arc by the quadruply imaged sample has demonstrate the higher SNR level (see the Figure~\ref{fig:image_inference}, ``Residual of the lensed arcs'' panel). Apparently, the lensed AGNs have a great potential  to extend to study the \mbh-\mstar\ at even higher redshift range.

@@

\subsection{WFI2033}\label{app:WFI2033}
WFI2033 is also observed by other four band data including WFC3/F125W (GO-12874; PI: D. Floyd), WFC3/F140W (GO-13732; PI: A. Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C. S. Kochanek). Similar to Section~\ref{app:HE0435}, the inference of the lensed arcs of WFI2033 have been fitted through five band. The lensed models are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d). Note that, limited by its exposure time, the data quality by F125W is not ideal and the host information could not be well extracted. Thus, we does not take the inference by F125W into account in the color inference. Finally, we find the stellar population with 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).
\begin{figure*}
\centering
\subfloat[WFI2033 F125W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
\subfloat[WFI2033 F140W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
\caption{\label{fig:app_WFI2033} 
Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The inference of the lensed arcs is not clear in the F125W data, and thus the SED fitting is done through the other four bands.}
\end{figure*} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Our work, one more time, confirmed the fidelity of using strong lensing as a tool to study the scaling relation at high redshift. The lensed AGN host galaxy can be accurately recovered using the state-of-the-art lens modelling technique. Even more, with a higher lens magnification effect, the lensed arc by the quadruply imaged sample has demonstrate the higher SNR level (see the Figure~\ref{fig:image_inference}, ``Residual of the lensed arcs'' panel). Apparently, the lensed AGNs have a great potential to extend to study the \mbh-\mstar\ at even higher redshift range.

@@

\subsection{WFI2033}\label{app:WFI2033}
WFI2033 is also observed by other four band data including WFC3/F125W (GO-12874; PI: D. Floyd), WFC3/F140W (GO-13732; PI: A. Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C. S. Kochanek). Similar to Section~\ref{app:HE0435}, the inference of the lensed arcs of WFI2033 have been fitted through five band. The lensed models are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d). Note that, limited by its exposure time, the data quality by F125W is not ideal and the host information could not be well extracted. Thus, we does not take the inference by F125W into account in the color inference. Finally, we find the stellar population with 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).
\begin{figure*}
\centering
\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
\caption{\label{fig:app_WFI2033} 
Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The inference of the lensed arcs is not clear in the F125W data, and thus the SED fitting is done through the other four bands.}
\end{figure*} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
